\documentclass[a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \usepackage{hyperref}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.6in,right=0.6in,bottom=0.4in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	\textbf{\Huge \scshape {Mahesh Natamai}} \\
	maheshkumar.natamai@gmail.com $\cdot$ maheshnatamai.com \\ linkedin.com/in/mahesh-natamai $\cdot$ github.com/MaheshNat $\cdot$ devpost.com/maheshkumar-natamai\\
\end{center}

%==== Education ====%
\header{Education}
\textbf{Georgia Institute Of Technology}\hfill  Expected Graduation: Dec 2024\\
BS Computer Science \textit{GPA: 4.0} \hfill \textit{Atlanta, GA} \\ 
\vspace{1mm} 
\textbf{Relevant Coursework:}
 Data Structures And Algorithms, Applied Combinatorics, Discrete Mathematics, Linear Algebra, Computer Organization And Programming (C \& Assembly), Multivariable Calculus\\
\vspace{1mm} 

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}

\textbf{Brains 4 Drones} \hfill Jun 2021 - Sep 2021\\
\textit{Computer Vision Intern} \hfill \textit{Plano, TX} \\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Led project systematically testing novel keypoint detection/description algorithms for simultaneous localization and mapping (SLAM) on autonomous drones.
	\item \textbf{Increased accuracy of keypoint matching algorithm by 15\%} by variating standard algorithm.
        \item Developed custom algorithm to efficiently select photos for drone camera calibration from 5-dimensional point cloud, \textbf{reducing calibration times by $\sim{}$10-20 seconds}.
	\item Simulated drone hardware pipeline for keypoint descriptor experiments using python and jupyter notebooks. Vectorized implementations using numpy for a \textbf{>10x speedup}. Utilized Robot Operating System (ROS) to interface with collected bag data.
\end{itemize}
\textbf{Fiverr} \hfill Nov 2020 - Jun 2021\\
\textit{Discord Bot Developer} \hfill \textit{Plano, TX} \\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Seller with over \textbf{18k impressions}, \textbf{30+ clients}, and a \textbf{5.0 star rating} for Node.js discord bot development.
	\item Integrated 3rd party APIs (twitch, hosting services, custom servers, etc.), using MongoDB and MySQL.
\end{itemize}

\header{Projects}
\vspace*{1mm}
{\textbf{AI Powered Video Search}} {\sl Python, Flask, Pytorch, React.js, Tailwind} \hfill \url{https://getscry.tech} \\
\begin{itemize} \itemsep -1pt
	\item Architected web app leveraging OpenAI's machine learning models to search through video frames and audio transcripts with natural language prompts, enabling surveillance systems to be easily navigable.
        \item Used ANNOY index to efficiently compute similarity scores. Created custom video downloading, diarization, transcription, and embedding generation pipeline.
        \item Currently analyzing video to combat pain points in existing camera surveillance systems. Transfer learning existing models to improve accuracy on incident detection tasks.
\end{itemize}
{\textbf{Sign Language Classifier}} {\sl Next.js, Python, Flask, Tensorflow} \hfill \url{https://github.com/MaheshNat/Signify}\\
\begin{itemize} \itemsep -1pt
	\item Designed ML model and web app to enable members of the deaf and hard of hearing communities to communicate with those who do not understand ASL (American Sign Language) using machine learning.
	\item Leverages custom-trained convolutional neural network (CNN) built using Tensorflow to translate ASL.
\end{itemize}
\vspace*{1mm}
{\textbf{Skill Bartering Platform}} {\sl MongoDB, React.js, Node.js} \hfill \url{https://github.com/MaheshNat/Menter}\\
\begin{itemize} \itemsep -1pt
	\item Architected during a hackathon as an education tool for skill bartering, i.e. allowing students to learn skills if they have something to teach in return.
\end{itemize}
\vspace*{1mm}

%==== Volunteering/Clubs ====%
\header{Research/Clubs}
\vspace{1mm}

\textbf{Undergraduate Researcher} \hfill Jan 2023 - Present\\
\textit{Georgia Institute Of Technology} \hfill \textit{Atlanta, GA} \\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Under Dr. Polo Chau: Creating an application for users to easily interface with inpainting and outpainting using stable diffusion. Using Python, Flask, Stable Diffusion, CLIP Segmentation, Next.js, and Tailwind.
\end{itemize}

\textbf{Fullstack Engineer} \hfill Aug 2022 - Present\\
\textit{Bits Of Good} \hfill \textit{Atlanta, GA} \\
\vspace{-1mm}
\begin{itemize} \itemsep -1pt
	\item Developed platform for nonprofit "Motherhood Beyond Bars" enabling incarcerated women to communicate with their children and receive necessary products. Using Next.js and Firebase. Currently on project maintainence team performing feature additions to mostly completed projects.
\end{itemize}

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages: & Python Java JavaScript TypeScript Node.js HTML CSS           \\
	Web Frameworks/Libraries:  & React/Redux Next.js Angular Flask Express.js Firebase \\
	Data Science:          & Numpy Pandas Tensorflow Matplotlib OpenCV                           \\
	Misc:             & MongoDB MySQL PostgreSQL Agile Git Linux                       \\
\end{tabular}
\vspace{2mm}

% \header{Awards}
% \textbf{First place in the tech category, most voted} \hfill Jumpstart Edtech Hackathon\\
% Won first place in the tech category and most voted out of 200 participants for my team’s submission to the Jumpstart Edtech startup competition/hackathon: Menter.\\
% \vspace*{2mm}
% \textbf{First place} \hfill Congressional App Challenge\\
% Won first place for Signify, an app submitted to the congressional app challenge\\

\ 
\end{document}